### 2019-08-16 EJSSubmission/WeightedSIgn_EJS_DA_02_24_19_1.tex
revision sent to kodu da

We apply the above outlier detection method on two data sets. First, we consider the 
monthly average \textit{sea surface temperature anomaly data} 
from June 1970 to May 2004, available 
from \url{http://www.cpc.ncep.noaa.gov/data/}, depicted in  panel (a) 
of Figure~\ref{fig:fPCAfig})).
Second, we consider the \textit{octane data}, which consists of 226 variables and 39 
observations \citep{ref:EsbensenetalBook94}. 
Each sample is a gasoline compound with a certain octane 
number, and has its NIR absorbance spectra measured in 2 nm intervals between 1100 - 1550 
nm. There are 6 outliers here: compounds 25, 26 and 36-39, which contain alcohol. This 
data is presented in  panel (b) of Figure~\ref{fig:fPCAfig})).

>>>>

We apply the above outlier detection method on two data sets. First, we consider the 
monthly average \textit{sea surface temperature anomaly data} 
from June 1970 to May 2004, available 
from \url{http://www.cpc.ncep.noaa.gov/data}, depicted in  panel (a) 
of Figure~\ref{fig:fPCAfig})).
Second, we consider the \textit{octane data}, which consists of 226 variables and 39 
observations \citep{ref:EsbensenetalBook94}. 
Each sample is a gasoline compound with a certain octane 
number, and has its NIR absorbance spectra measured in 2 nm intervals between 1100 - 1550 
nm. There are 6 outliers here: compounds 25, 26 and 36-39, which contain alcohol. This 
data is presented in  panel (b) of Figure~\ref{fig:fPCAfig})).

### 2019-08-16 EJSSubmission/WeightedSign_EJS_Dispersion_02_24_19_1.tex
cor 2.2 fixed
revision sent to kodu da

\section{A Robust Measure of  Dispersion} 
\label{Sec:WSDispersion1}

From this section onwards, we assume that $\cX = \BR^{p}$, that is, the support of the 
random variable under study is the $p$-dimensional Euclidean plane, and the data 
$X_{1}, \ldots, X_{n}$ are independent and identically distributed from an 
elliptical distribution $\BF$ with parameters $\mu$ and $\Sigma$.  We also 
assume that $X_{1}$ is absolutely continuous, with $\BP [ | X_{1}| = 0] = 0$, 
and that $\Sigma$ is positive definite. This  eliminates technicalities arising from
 rank deficient cases, and makes the weight functions  affine invariant.
Thus, we essentially restrict the rest of this paper to the same  framework as in 
Corollary~\ref{Cor:Elliptic_ARE}. Most of the results below generalize to the case where 
$\cX$ is a separable Hilbert space, however additional technicalities are involved, as in 
\cite{ref:AoS112852_Balietal_PCA_Functional_Robust}, and will be considered 
in a future project.

Consider the spectral decomposition of $\Sigma$ given by
 $\Sigma = \Gamma\Lambda\Gamma^T$, where $\Gamma$ is an orthogonal matrix 
 and $\Lambda$ is diagonal with positive diagonal elements $\lambda_1 \geq \ldots \geq 
 \lambda_p$.
Also denote the $i$-th eigenvector of $\Sigma$ by 
$\bfgamma_{i} = (\gamma_{i, 1}, \ldots, \gamma_{i, p})^T$ for $1 \leq i \leq p$. Thus, the 
$i$-th column of $\Gamma$ is $\bfgamma_{i}$.
  In the rest of this paper we use the notation 
 $\Sigma^{-1/2} = \Lambda^{-1/2} \Gamma^{T}$, and 
 hence $Z = \Lambda^{-1/2} \Gamma^T (X - \mu)$. 
Recall from Section~\ref{Sec:WSQuantiles} that we use the notation $\BF_{Z}$ for 
the distribution of $Z$, and that $\BF_{Z}$ is a spherically symmetric distribution 
and hence depends only on $|z|$.
Additionally, to simplify notations, for any random variable $X \sim \BF$, we occasionally 
use the abbreviated notation $W (X) \equiv W (X, \BF)$. Note that $W (X)$ is a 
\textit{random weight}, and takes the same value as $W (Z, \BF_{Z})$.  
Also, as noted in  Corollary~\ref{Cor:Elliptic_ARE}, 
 $W (Z)$ is a function of $|Z|$ only. 
 We additionally assume that $\BE W^{2} (X) < \infty$.

@@

The rest of this paper is built on the following transformed random variable:
\baq
\tilde{X} = W (X, \BF) S(X; \mu) \equiv W (Z, \BF_{Z})  
| \Lambda^{1/2} Z|^{-1} \Gamma \Lambda^{1/2}  Z. 
\label{eq:tildeX}
\eaq
We define the notation $\BS (X; \mu) =  S (X; \mu) S( X; \mu)^T$.
Then, we define the following dispersion  parameter:
\baq
\tilde{\Sigma} = \BE \tilde{X} \tilde{X}^{T}
=  \BE W^{2} (X, \BF) \BS (X; \mu). 
\label{eq:tildeSigma}
\eaq
 In the following Theorem, we establish that the eigenvectors of ${\Sigma}$ and 
 $\tilde{\Sigma}$ are identical, although their eigenvalues may be different.

@@

Also, since the weight $W(X)$ is a function of $|Z| = R$, we have that $W(X)$ is 
independent of $S (X; \mu)$. Consequently, we have  
  \ban
  \tilde{\Sigma} & = \BE \tilde{X} \tilde{X}^{T} 
%  \\
%&
 = \BE W^{2} (X) S (X; \mu) S(X; \mu)^{T} \\
& =  \BE W^{2} (X)  \BE S (X; \mu) S(X; \mu)^{T} 
%\\
%& 
= \Gamma \Lambda_{W} \Gamma^{T}, 
\ean
where $\Lambda_{W}$ is a diagonal matrix.

We now discuss the properties of the sample version $\widehat{\tilde{\Sigma}}$ 
computed from $\bfX$. 
In practice, we cannot obtain $W (x) \equiv W (x, \BF)$, 
and consequently use  $W (x, \BF_{n})$ instead. We assume the following conditions:
\begin{enumerate}
\item \textbf{Bounded weights:} The weights $W (\cdot, \cdot)$ are bounded functions.

\item \textbf{Uniform convergence:} 
\ban 
\sup_{x \in \cX} | W (x, \BF_{n}) - W (x, \BF) | \rightarrow 0 
\ean 
almost surely as $n \rightarrow \infty $.

\item \textbf{Smoothness under perturbation:}
For all $\BF \in \cF$, there exists a $\delta > 0$, possibly depending on $\BF$, such that 
for any $\epsilon \in (0, \delta)$ 
\ban 
\sup_{x \in \cX} \Bigl| W \bigl( x, \BF \bigr) - 
W \bigl( x, (1 - \epsilon)\BF + \epsilon \delta_{x} \bigr) \Bigr| \leq 
\epsilon.
\ean 
 \end{enumerate}
 In the above, $\delta_{x}$ denotes point mass at $x$. 
These property are easily satisfied under for  weight functions  derived 
from standard depth functions, for example, $W_{HSD} (\cdot)$, 
$W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.

The following result allows us to use the empirical, plug-in weights and an 
estimated location parameter in the 
weighted dispersion estimator. A natural choice for the location parameter estimator 
is the solution to $\sum_{i = 1}^{n} \tilde{X}_{i} = 0$.

@@

Notice that the $(j, k)$-th element of $T_{2}$ is given by 
\ban 
n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ W_{n}^{2} (X_{i}, \BF_{n})  -   W^{2} (X_{i}, \BF) \bigr\} 
(X_{i, j} - \mu_{j}) (X_{i, k} - \mu_{k}), 
\ean
and hence 
\ban 
& c^{T} T_{2} c  = \sum_{j, k} c_{j} c_{k}T_{2, j, k} \\
& = n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ W_{n}^{2} (X_{i}, \BF_{n})  -   W^{2} (X_{i}, \BF) \bigr\} 
\bigl( \sum_{j} c_{j} (X_{i, j} - \mu_{j}) \bigr)^{2} \\
& \leq 
M n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ | W_{n} (X_{i}, \BF_{n})  -   W (X_{i}, \BF) | \bigr\} 
\bigl( c^{T} (X_{i} - \mu) \bigr)^{2} \\
& \leq 
M n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ | W_{n} (X_{i}, \BF_{n})  -   W_{n} (X_{i}, \BF_{n, -i})  | \bigr\} 
\bigl( c^{T} (X_{i} - \mu) \bigr)^{2} 
\\ & \hspace{1cm}
+ M n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ | W_{n} (X_{i}, \BF_{n, -i})  -   W (X_{i}, \BF) | \bigr\} 
\bigl( c^{T} (X_{i} - \mu) \bigr)^{2} 
\\
& =  M n^{-1} \sum_{i=1}^{n}  T_{2 1 i}  + M n^{-1} \sum_{i=1}^{n}   T_{2 2 i} \\
& = T_{21} + T_{22}.
\ean
Let $H (X_{i}) = | X_{i} - \mu |^{-2} \bigl( c^{T} (X_{i} - \mu) \bigr)^{2}$, and notice 
that $H (X_{i}) \leq 1$ almost surely for $|c| = 1$.  
Now notice that conditional on $X_{i}$ except for a null set $A_{i}$ (possibly depending 
on $X_{i}$) we have  
$T_{2 1 i} \leq n^{-1}  H (X_{i}) $. Thus, except for a null set 
$A_{1} \cap \ldots \cap A_{n}$, $T_{21} \leq M n^{-2}  H (X_{i})$ and the conclusion 
follows for this part.

@@

Let $vec~(\BS (X; \mu))$ be the vectorized version of  $\BS (X; \mu)$.
We are now in a position to state the result for consistency of the sample 
version of $\tilde{\Sigma}$,

\begin{Theorem} \label{Theorem:CLT1}
Assume the conditions of Lemma~\ref{Lemma:lemma1}. Then
\ban
& n^{1/2} \sum_{i = 1}^{n} \Bigl( 
W_{n}^{2} (X_{i}, \BF_{n}) ~vec~(\BS (X_{i}; \hat{\mu}_{n})) 
- \BE W^{2} (X_{i}) ~vec~(\BS (X_{i}; \mu)) \Bigr)\\
& \hspace{0.5cm} \draro
N_{p^2} \bigl( 0, V_{W} \bigr),
\ean
where $V_{W} = \BV [W^{2} (X_{i}, \BF) ~vec~(\BS (X_{i}; {\mu})) ] $.
\end{Theorem}

@@

\section{An Affine Equivariant Robust Measure of Dispersion}
\label{Sec:WSDispersion2}

A desirable invariance property of any dispersion parameter $T_{X}$ corresponding to 
a random variable $X$ is that under affine transformation $Y = AX + b$ the dispersion 
parameter scales to $T_{Y} = A T_{X} A^{T}$. It is clear that $\tilde{\Sigma}$ does 
not possess this property, since it remains unchanged for $X$ and $Y = c X$ for any 
scalar $c > 0$.

@@

\vspace{1em}
\noindent\textbf{(C1)} The function $u(r)/r^2$ is monotone decreasing, 
and $u(r)>0$ for $r > 0$;

\noindent\textbf{(C2)}  The function $v(r)$ is monotone decreasing, and 
$v(r) > 0$ for $r > 0$;

\noindent\textbf{(C3)} Both $u(r)$ and $v(r)$ are bounded and continuous;

\noindent\textbf{(C4)} $u(0) / v(0) < p$;

\noindent\textbf{(C5)} For any hyperplane in the sample space $\mathcal X$, 
(i) $P(H) = \BE \{ \cI_{\{X \in H \}} \} < 1 - p v(\infty) / u(\infty)$ and 
(ii) $P(H) \leq 1/p$.
%

\vspace{1em}
\noindent Putting things into context, in our case we have 
$v (\cdot) = p^{-1}\BV W (X)$, 
$u (\cdot) = W^{2}(X)$. 
%We use the notation $\BF_{|Z|}$ for the cumulative distribution function of $|Z|$.
We proceed to verify the other conditions for the weight functions 
$W_{HSD} (\cdot)$, 
$W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.

@@

In order to compute the sample version of $\Sigma_{*}$, we solve (\ref{eqn:ADCM}) 
iteratively by obtaining a sequence of positive definite matrices 
$\hat{\Sigma}^{(k)}_{*}$ until convergence. Thus, using the location 
estimator $\hat{\mu}_{n}$, we may iterate
%
\ban
\hat{\Sigma}^{(k+1)}_{*}  = 
\frac{p}{ \BV W (X) } 
\BE \left[ \frac{W^{2}(X) (X - \hat{\mu}_{n}) (X - \hat{\mu}_{n})^T}
{(X - \hat{\mu}_{n})^T (\hat{\Sigma}^{(k)}_{*})^{-1}(X - \hat{\mu}_{n})} \right].
\ean
%

@@

\section{Robust Estimation of Eigenvalues, and a Plug-in Estimator of $\Sigma$}
\label{Sec:Eigen}

As seen in Theorem~\ref{Thm:WSVariance}, eigenvalues of the $\tilde{\Sigma}$ 
are not same as the population eigenvalues. In this section, we discuss on robust 
estimation of $\lambda_{i}$'s using $\tilde{\Sigma}$. Assume the data 
is centered, the robust estimator from Section~\ref{Sec:WSQuantiles} suffices. 
We start by computing 
the sample version $\widehat{\tilde{\Sigma}}$ and its spectral decomposition:
\ban 
\widehat{\tilde{\Sigma}} = \widehat{{\Gamma}} \widehat{\tilde{\Lambda}}
\widehat{{\Gamma}}^{T}
\ean 
We then use the following steps:

@@

\begin{proof}[Proof of Theorem \ref{Thm:pluginSigma}]
This proof has many algebraic steps, and we sketch the main arguments below.
Suppose $\hat{A} = \widehat{{\Gamma}}^{T}  \Sigma \widehat{{\Gamma}}$.

Owing to the fact that the Frobenius norm is invariant under rotations and 
that $p$ is finite and fixed, it suffices to show that the off-diagonal elements of 
$\hat{A}$ converge in probability to zero, and that the difference between 
the $i$-th diagonal element of $\hat{A}$ and ${\lambda}^{\dagger}_{i}$ converges to 
zero for any $i = 1, \ldots, p$.

Now notice that from Theorem~\ref{Theorem:Eigen1} we have that $\widehat{{\Gamma}} 
= {{\Gamma}} + R_{n1}$, where the $(i, j)$-th element of the remainder 
$R_{n1, i, j}$ satisfies $\BE  R_{n1, i, j}^{2} = O(n^{-1})$.

We can show, using standard algebra, that 
\ban
\hat{A} = \Lambda + R_{n2}, 
\ean
where the $(i, j)$-th element of the remainder 
$R_{n2, i, j}$ satisfies $\BE  R_{n2, i, j}^{2} = O(n^{-1})$. 
This follows immediately from above, the fact that $p$ is finite and fixed, and all 
elements of $\Lambda$ are constants. This immediately establishes the case for the 
off-diagonal elements.

>>>>

\section{A robust measure of dispersion} 
\label{Sec:WSDispersion1}
From this section onwards, we assume that $\cX = \BR^{p}$, that is, the support of the 
random variable under study is the $p$-dimensional Euclidean plane, and the data 
$X_{1}, \ldots, X_{n}$ are independent and identically distributed from an 
elliptical distribution $\BF$ with parameters $\mu$ and $\Sigma$.  We also 
assume that $X_{1}$ is absolutely continuous, with $\BP [ | X_{1}| = 0] = 0$, 
and that $\Sigma$ is positive definite. This  eliminates technicalities arising from
 rank deficient cases, and makes the weight functions  affine invariant.
Thus, we essentially restrict the rest of this paper to the same  framework as in 
Corollary~\ref{Cor:Elliptic_ARE}. Most of the results below generalize to the case where 
$\cX$ is a separable Hilbert space, however additional technicalities are involved, as in 
\cite{ref:AoS112852_Balietal_PCA_Functional_Robust}, and will be considered 
in a future project.

\subsection{The Weighted Sign Covariance Matrix}
Consider the spectral decomposition of $\Sigma$ given by
 $\Sigma = \Gamma\Lambda\Gamma^T$, where $\Gamma$ is an orthogonal matrix 
 and $\Lambda$ is diagonal with positive diagonal elements $\lambda_1 \geq \ldots \geq 
 \lambda_p$.
Also denote the $i$-th eigenvector of $\Sigma$ by 
$\bfgamma_{i} = (\gamma_{i, 1}, \ldots, \gamma_{i, p})^T$ for $1 \leq i \leq p$. Thus, the 
$i$-th column of $\Gamma$ is $\bfgamma_{i}$.
  In the rest of this paper we use the notation 
 $\Sigma^{-1/2} = \Lambda^{-1/2} \Gamma^{T}$, and 
 hence $Z = \Lambda^{-1/2} \Gamma^T (X - \mu)$. 
Recall from Section~\ref{Sec:WSQuantiles} that we use the notation $\BF_{Z}$ for 
the distribution of $Z$, and that $\BF_{Z}$ is a spherically symmetric distribution 
and hence depends only on $|z|$.
Additionally, to simplify notations, for any random variable $X \sim \BF$, we occasionally 
use the abbreviated notation $W (X) \equiv W (X, \BF)$. Note that $W (X)$ is a 
\textit{random weight}, and takes the same value as $W (Z, \BF_{Z})$.  
Also, as noted in  Corollary~\ref{Cor:Elliptic_ARE}, 
 $W (Z)$ is a function of $|Z|$ only. 
 We additionally assume that $\BE W^{2} (X) < \infty$.

@@

The rest of this paper is built on the following transformed random variable:
\baq
\tilde{X} = W (X, \BF) S(X; \mu) \equiv W (Z, \BF_{Z})  
| \Lambda^{1/2} Z|^{-1} \Gamma \Lambda^{1/2}  Z. 
\label{eq:tildeX}
\eaq
We fix the notation $\BS (X; \mu) =  S (X; \mu) S( X; \mu)^T$, and define the following dispersion  parameter:
\baq
\tilde{\Sigma} = \BE \tilde{X} \tilde{X}^{T}
=  \BE W^{2} (X, \BF) \BS (X; \mu). 
\label{eq:tildeSigma}
\eaq
In the following Theorem, we establish that the eigenvectors of ${\Sigma}$ and $\tilde{\Sigma}$ are identical, although their eigenvalues may be different.

@@

Also, since the weight $W(X)$ is a function of $|Z| = R$, we have that $W(X)$ is 
independent of $S (X; \mu)$. Consequently, we have  
  \ban
  \tilde{\Sigma} & = \BE \tilde{X} \tilde{X}^{T} 
%  \\
%&
 = \BE W^{2} (X) S (X; \mu) S(X; \mu)^{T} \\
& =  \BE W^{2} (X)  \BE S (X; \mu) S(X; \mu)^{T} 
%\\
%& 
= \Gamma \Lambda_{W} \Gamma^{T}, 
\ean
where $\Lambda_{W}$ is a diagonal matrix.
\end{proof}

\subsection{Sample version of $\tilde \Sigma$}
We now discuss the properties of the sample version of $\tilde \Sigma$, say $\widehat{\tilde{\Sigma}}$ computed from $\bfX$. In practice, we cannot obtain $W (x) \equiv W (x, \BF)$, and consequently use  $W (x, \BF_{n})$ instead. We assume the following conditions:

\begin{description}
\item[(B1)]{\it Bounded weights}: The weights $W (\cdot, \cdot)$ are bounded functions.

\item[(B2)]{\it Uniform convergence}:
\ban 
\sup_{x \in \cX} | W (x, \BF_{n}) - W (x, \BF) | \rightarrow 0 
\ean 
almost surely as $n \rightarrow \infty $.

\item[(B3)]
{\it Smoothness under perturbation:} For all $\BF \in \cF$, there exists a $\delta > 0$, possibly depending on $\BF$, such that 
for any $\epsilon \in (0, \delta)$ 
\ban 
\sup_{x \in \cX} \Bigl| W \bigl( x, \BF \bigr) - 
W \bigl( x, (1 - \epsilon)\BF + \epsilon \delta_{x} \bigr) \Bigr| \leq 
\epsilon.
\ean 
\end{description}
%
In the above, $\delta_{x}$ denotes point mass at $x$. 
These properties are easily satisfied under for  weight functions  derived from standard depth functions, for example, $W_{HSD} (\cdot)$, $W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.

The following result allows us to use the empirical, plug-in weights and an estimated location parameter in the weighted dispersion estimator. A natural choice for the location parameter estimator is the solution to $\sum_{i = 1}^{n} \tilde{X}_{i} = 0$, which is the same as the sample version of the weighted spatial median discussed in Section~\ref{Sec:WSQuantiles}.

@@

Notice that the $(j, k)$-th element of $T_{2}$ is given by 
\ban 
n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ W_{n}^{2} (X_{i}, \BF_{n})  -   W^{2} (X_{i}, \BF) \bigr\} 
(X_{i, j} - \mu_{j}) (X_{i, k} - \mu_{k}), 
\ean
%
and hence 
%
\ban 
& c^{T} T_{2} c  = \sum_{j, k} c_{j} c_{k}T_{2, j, k} \\
& = n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ W_{n}^{2} (X_{i}, \BF_{n})  -   W^{2} (X_{i}, \BF) \bigr\} 
\bigl( \sum_{j} c_{j} (X_{i, j} - \mu_{j}) \bigr)^{2} \\
& \leq 
M n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ | W_{n} (X_{i}, \BF_{n})  -   W (X_{i}, \BF) | \bigr\} 
\bigl( c^{T} (X_{i} - \mu) \bigr)^{2} \\
& \leq 
M n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ | W_{n} (X_{i}, \BF_{n})  -   W_{n} (X_{i}, \BF_{n, -i})  | \bigr\} 
\bigl( c^{T} (X_{i} - \mu) \bigr)^{2} 
\\ & \hspace{1cm}
+ M n^{-1} \sum_{i=1}^{n}  | X_{i} - \mu |^{-2}
\bigl\{ | W_{n} (X_{i}, \BF_{n, -i})  -   W (X_{i}, \BF) | \bigr\} 
\bigl( c^{T} (X_{i} - \mu) \bigr)^{2} 
\\
& =  M n^{-1} \sum_{i=1}^{n}  T_{2 1 i}  + M n^{-1} \sum_{i=1}^{n}   T_{2 2 i} \\
& = T_{21} + T_{22}.
\ean
%
Let $H (X_{i}) = | X_{i} - \mu |^{-2} \bigl( c^{T} (X_{i} - \mu) \bigr)^{2}$, and notice 
that $H (X_{i}) \leq 1$ almost surely for $|c| = 1$.  
Now notice that conditional on $X_{i}$ except for a null set $A_{i}$ (possibly depending 
on $X_{i}$) we have  
$T_{2 1 i} \leq n^{-1}  H (X_{i}) $. Thus, except for a null set 
$A_{1} \cap \ldots \cap A_{n}$, $T_{21} \leq M n^{-2}  H (X_{i})$ and the conclusion 
follows for this part.

@@

Let $vec(\BS (X; \mu))$ be the vectorized version of  $\BS (X; \mu)$.
We are now in a position to state the result for consistency of the sample 
version of $\tilde{\Sigma}$,

\begin{Theorem} \label{Theorem:CLT1}
Assume the conditions of Lemma~\ref{Lemma:lemma1}. Then
\ban
& n^{1/2} \sum_{i = 1}^{n} \Bigl( 
W_{n}^{2} (X_{i}, \BF_{n}) vec(\BS (X_{i}; \hat{\mu}_{n})) 
- \BE W^{2} (X_{i}) vec(\BS (X_{i}; \mu)) \Bigr)\\
& \hspace{0.5cm} \draro
N_{p^2} \bigl( 0, V_{W} \bigr),
\ean
where $V_{W} = \BV [W^{2} (X, \BF) vec(\BS (X; {\mu})) ] $.
\end{Theorem}

@@

\section{An affine equivariant robust measure of dispersion}
\label{Sec:WSDispersion2}
A desirable invariance property of any dispersion parameter $T_{X}$ corresponding to 
a random variable $X$ is that under affine transformation $Y = AX + b$ the dispersion 
parameter scales to $T_{Y} = A T_{X} A^{T}$. It is clear that $\tilde{\Sigma}$ does 
not possess this property, since it remains unchanged for $X$ and $Y = c X$ for any 
scalar $c > 0$.

@@

\begin{description}
\item[(C1)] The function $u(r)/r^2$ is monotone decreasing, 
and $u(r)>0$ for $r > 0$;

\item[(C2)]  The function $v(r)$ is monotone decreasing, and 
$v(r) > 0$ for $r > 0$;

\item[(C3)] Both $u(r)$ and $v(r)$ are bounded and continuous,

\item[(C4)] $u(0) / v(0) < p$,

\item[(C5)] For any hyperplane in the sample space $\mathcal X$, 
(i) $P(H) = \BE \{ \cI_{\{X \in H \}} \} < 1 - p v(\infty) / u(\infty)$ and 
(ii) $P(H) \leq 1/p$.
\end{description}

Putting things into context, in our case we have 
$v (\cdot) = p^{-1}\BV W (X)$, 
$u (\cdot) = W^{2}(X)$. 
%We use the notation $\BF_{|Z|}$ for the cumulative distribution function of $|Z|$.
We proceed to verify the other conditions for the weight functions 
$W_{HSD} (\cdot)$, 
$W_{MhD} (\cdot)$ and $W_{PD} (\cdot)$ discussed earlier.

@@

To compute the sample version of $\Sigma_{*}$, we solve (\ref{eqn:ADCM}) 
iteratively by obtaining a sequence of positive definite matrices 
$\hat{\Sigma}^{(k)}_{*}$ until convergence. Thus, using the location 
estimator $\hat{\mu}_{n}$, we may iterate
%
\ban
\hat{\Sigma}^{(k+1)}_{*}  = 
\frac{p}{ \BV W (X) } 
\BE \left[ \frac{W^{2}(X) (X - \hat{\mu}_{n}) (X - \hat{\mu}_{n})^T}
{(X - \hat{\mu}_{n})^T (\hat{\Sigma}^{(k)}_{*})^{-1}(X - \hat{\mu}_{n})} \right].
\ean
%

@@

\section{Robust estimation of eigenvalues, and a plug-in estimator of $\Sigma$}
\label{Sec:Eigen}
As seen in Theorem~\ref{Thm:WSVariance}, eigenvalues of the $\tilde{\Sigma}$ 
are not same as the population eigenvalues. In this section, we discuss on robust 
estimation of $\lambda_{i}$'s using $\tilde{\Sigma}$. Assume the data 
is centered, the robust estimator from Section~\ref{Sec:WSQuantiles} suffices. 
We start by computing 
the sample version $\widehat{\tilde{\Sigma}}$ and its spectral decomposition:
\ban 
\widehat{\tilde{\Sigma}} = \widehat{{\Gamma}} \widehat{\tilde{\Lambda}}
\widehat{{\Gamma}}^{T}
\ean 
We then use the following steps:

@@

\begin{proof}[Proof of Theorem \ref{Thm:pluginSigma}]
This proof has many algebraic steps, and we sketch the main arguments below.

Suppose $\hat{A} = \widehat{{\Gamma}}^{T}  \Sigma \widehat{{\Gamma}}$.  Owing to the fact that the Frobenius norm is invariant under rotations and that $p$ is finite and fixed, it suffices to show that the off-diagonal elements of $\hat{A}$ converge in probability to zero, and that the difference between the $i$-th diagonal element of $\hat{A}$ and ${\lambda}^{\dagger}_{i}$ converges to zero for any $i = 1, \ldots, p$.

Now notice that from Theorem~\ref{Theorem:Eigen1} we have that $\widehat{{\Gamma}} 
= {{\Gamma}} + R_{n1}$, where the $(i, j)$-th element of the remainder 
$R_{n1, i, j}$ satisfies $\BE  R_{n1, i, j}^{2} = O(n^{-1})$. We can show, using standard algebra, that 
\ban
\hat{A} = \Lambda + R_{n2}, 
\ean
where the $(i, j)$-th element of the remainder 
$R_{n2, i, j}$ satisfies $\BE  R_{n2, i, j}^{2} = O(n^{-1})$. 
This follows immediately from above, the fact that $p$ is finite and fixed, and all 
elements of $\Lambda$ are constants. This immediately establishes the case for the 
off-diagonal elements.

### 2019-08-16 EJSSubmission/WeightedSign_EJS_IF_02_24_19_1.tex
revision sent to kodu da

\begin{proof}[Proof of Proposition~\ref{Thm:IF2}:]

Let $z_{0} = \Lambda^{-1/2} \Gamma^T  (x_0 - \mu) = (z_{0 1}, \ldots, z_{0 p})^T$.
As a first step, since $\Sigma_{*}$ is affine equivariant, we obtain from 
\cite{ref:Biometrika00603_CrouxHaesbroeck} 
that 
\ban 
IF ( x_{0}, \Sigma_{*}, \BF) = \Sigma_{*}^{1/2} 
IF ( z_{0}, \Sigma_{*}, \BF_{Z})  \Sigma_{*}^{1/2}.
\ean
From Lemma1 of \citep{ref:HampelBook86}, page 276, we obtain that there exist 
scalar valued functions $\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} )$ and 
$\beta_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) $ such  that 
\ban
IF ( z_{0}, \Sigma_{*}, \BF_{Z}) = \alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) 
\BS( z_0; {\mathbf 0}) 
- \beta_{\Sigma_{*}} (| x_{0} |; \BF_{Z} ) \BI_{p}, 
\ean
consequently we obtain
\ban 
IF ( x_{0}, \Sigma_{*}, \BF) = 
\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) 
\BS( x_0; \mu) 
- \beta_{\Sigma_{*}} (| x_{0} |; \BF_{Z} ) \Sigma_{*}.
\ean
\end{proof}

>>>>

\begin{proof}[Proof of Proposition~\ref{Thm:IF2}]
Let $z_{0} = \Lambda^{-1/2} \Gamma^T  (x_0 - \mu) = (z_{0 1}, \ldots, z_{0 p})^T$.
As a first step, since $\Sigma_{*}$ is affine equivariant, we obtain from 
\cite{ref:Biometrika00603_CrouxHaesbroeck} 
that 
\ban 
IF ( x_{0}, \Sigma_{*}, \BF) = \Sigma_{*}^{1/2} 
IF ( z_{0}, \Sigma_{*}, \BF_{Z})  \Sigma_{*}^{1/2}.
\ean
From Lemma 1 of \citep{ref:HampelBook86}, page 276, we obtain that there exist 
scalar valued functions $\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} )$ and 
$\beta_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) $ such  that 
\ban
IF ( z_{0}, \Sigma_{*}, \BF_{Z}) = \alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) 
\BS( z_0; {\mathbf 0}) 
- \beta_{\Sigma_{*}} (| x_{0} |; \BF_{Z} ) \BI_{p}, 
\ean
consequently we obtain
\ban 
IF ( x_{0}, \Sigma_{*}, \BF) = 
\alpha_{\Sigma_{*}} ( | x_{0} |; \BF_{Z} ) 
\BS( x_0; \mu) 
- \beta_{\Sigma_{*}} (| x_{0} |; \BF_{Z} ) \Sigma_{*}.
\ean
\end{proof}
